Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-02 TABLE/magnifications.tex
incorporated some comments from TT,RF,MJ: UNCERTAINTY CHANGE   *  This iteration includes a significant change in the measured magnification uncertainty,     correcting an oversight in prior versions (I had dropped the error term accounting for the     intrinsic scatter in SN Ia luminosities... thanks to Ryan and Saurabh for correction)

\begin{deluxetable*}{lccp{1.5in}p{2.2in}}
\tablecolumns{5}
\tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model} & \colhead{Best}\tablenotemark{a} & \colhead{Median\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
\startdata
%Sharon         & 2.57$^{+0.19}_{-0.16}$ &   \citealt{Jullo:2007} \\[2mm]
Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong lensing based model.\\
CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong+weak lensing based model.\\
Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32 & 2.28$^{+0.07}_{-0.11}$ &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
Zitrin-NFW   & 2.07 & 2.27$^{+0.23}_{-0.22}$ &   \citealt{Zitrin:2009a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model\\
Bradac(v2)   & 2.23 & 2.20$^{+0.03}_{-0.01}$ &   \citealt{Bradac:2005,Bradac:2009} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.}\\
Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
Diego\tablenotemark{i}			 & \nodata & 2.10$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
\enddata
\tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Uncertainties enclose 68\%\ of the realized values.}  
\tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
\tablenotetext{d}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{g}{{\tt GRALE} : }
\tablenotetext{h}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
\tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the Lam model.}}
\end{deluxetable*}

>>>>

\begin{deluxetable*}{lccp{1.5in}p{2.2in}}
\tablecolumns{5}
\tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model} & \colhead{Best}\tablenotemark{a} & \colhead{Median\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
\startdata
Sharon(v1)   & 2.53 & 2.57$^{+0.18}_{-0.16}$ & \citealt{Jullo:2007}  & LENSTOOL parametric, strong-lensing based model\\
Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric strong-lensing based model.\\
CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric model with both strong and weak lensing constraints.\\
Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32 & 2.28$^{+0.07}_{-0.11}$ &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
Zitrin-NFW   & 2.07 & 2.27$^{+0.23}_{-0.22}$ &   \citealt{Zitrin:2009a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model\\
Bradac(v2)   & 2.23 & 2.20$^{+0.03}_{-0.01}$ &   \citealt{Bradac:2005,Bradac:2009} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.}\\
Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
Diego\tablenotemark{i}			 & \nodata & 2.10$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
\enddata
\tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Uncertainties enclose 68\%\ of the realized values.}  
\tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
\tablenotetext{d}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{g}{{\tt GRALE} : }
\tablenotetext{h}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
\tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the Lam model.}}
\end{deluxetable*}

### 2015-04-02 snTomas.tex
incorporated some comments from TT,RF,MJ: UNCERTAINTY CHANGE   *  This iteration includes a significant change in the measured magnification uncertainty,     correcting an oversight in prior versions (I had dropped the error term accounting for the     intrinsic scatter in SN Ia luminosities... thanks to Ryan and Saurabh for correction)

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
SN has a projected separation from the cluster core of
$\sim$40\arcsec, closer to the critical lensing line than any previous
cluster-lensed \SNIa.  As such, it provides the first opportunity to
confront gravitational lens models of galaxy clusters with the direct
measurement of an absolute magnification at the edge of the
strong-lensing region.  We derive a tightly constrained measure of the
peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is $0.75\pm0.10$ magnitudes brighter than unlensed \SNeIa\ at similar
redshift, implying a lensing magnification of $\mu_{\rm
obs}=2.00\pm0.19$.  We compare this direct measurement of the
magnification against predicted magnifications from 11 lens models,
representing a broad range of methodologies and incorporating a
variety of strong- and weak-lensing constraints. 
The models are collectively fairly accurate, with 3 that are
consistent within the 1$\sigma$ uncertainties.
% a naive unweighted mean of  $\mu_{\rm mod}=2.6$.  
However, the models are systematically biased to higher values: none
of the tested models predict a magnification equal to or lower than
the observed $\mu$, and some models are more than $5\sigma$ above the
measured magnification.  We evaluate possible causes for this bias,
and find that intercomparison of the lens models rules out several
simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
single cluster could provide a robust evaluation of systematic biases
in lens models.  Until such a sample exists, it is advisable
to \change{increase the estimated uncertainty of predicted
magnifications to match the dispersion observed across multiple lens
models.}
\end{abstract}

@@

\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Quimby:2014}.}

@@

\change{
One of the key values in observing standard candles behind
gravitational lenses is that {\it all} lensing reconstructions suffer
from the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
degeneracy arises because one can introduce into a lens model an
unassociated sheet of mass in front of or behind the lens, without
disturbing the primary observable quantities.  For example, take a
lens model with a given surface mass density $\kappa$, and then
transform the surface mass density to
$\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
$\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$ models will
produce exactly the same values for all positional and shear
constraints from strong and weak lensing.  This is the simplest case
illustrating a positional constraint degeneracy, but there are more
complex versions \citep{Schneider:2014}.  Such mass sheet
degeneracies do not extend to the \citep{absolute} magnification of a
background source's flux and size.  Therefore, an absolute measurement
of magnification from a standard candle or a standard ruler
\citep{Sonnenfeld:2011}  can break this fundamental degeneracy
\citep{Holz:2001}.
}

@@

Another nearby bright galaxy to the East of the SN has a spectroscopic
redshift of $z=1.742$.  This redshift was determined from a spectrum
taken with the G141 grism of the HST WFC3-IR camera, collected as part
of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
and \ref{sec:PhotometricClassification}, the SN data are inconsistent
with that redshift, meaning that this nearby galaxy is a background
object and therefore has no impact on the SN classification or
luminosity measurement.}

@@

Final values for the SN distance modulus are shown in
Table~\ref{tab:MeasuredMagnification}, both for the spectroscopic
redshift ($z=1.31$) and the photometric redshift ($z=1.35$).  The two
light curve fitters are consistent within the uncertainties.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models. Solid vertical lines show the constraints from SN \tomas\
derived in Section~\ref{sec:Magnification} using the SALT2 (red) and
MLCS2k2 (blue) fitters, with shaded regions marking the total
uncertainty for each. Markers with horizontal error bars show the
median magnification and 68\%\ confidence region from each of the 10
lensing models.  Circles indicate models that use only strong-lensing
constraints, while diamonds denote those that also incorporate
weak-lensing measurements.  Models shown with open markers were
constructed using only data available before the start of the Frontier
Fields observations.  Filled markers indicate models that use
additional input constraints, including new multiply imaged systems
and redshifts.  The seven models shown in black at the top are from
the ``parametric'' family, and the four in green at the bottom are
``free-form.''  The dashed grey line marks the unweighted mean of all
model magnifications, with grey shading indicating the standard error
of the mean from naively assuming all are independent predictions.
\label{fig:lensingtest} }
\end{center}
\end{figure}

Table~\ref{tab:PredictedMagnifications} lists the 11 models, giving
for each one the predicted magnification and uncertainty for a source
at $z=1.31\pm0.01$ and at the position of \tomas.  These models
represent a broad sampling of the techniques and assumptions that can
be applied to the modeling of mass distributions in galaxy clusters. A
rigorous comparison of these disparate lens modeling techniques is
beyond the scope of this work. Table~\ref{tab:PredictedMagnifications}
includes a brief description of each model, but for a complete
discussion of the methodology the reader is referred to the listed
references.

In Figure~\ref{fig:lensingtest} the model predictions are plotted
alongside the observed magnification of SN \tomas, derived in
Section~\ref{sec:Magnification}.  This comparison shows that these 11
models are largely consistent with each other. Naively treating each
model as an independent prediction for the magnification (and ignoring
their quoted uncertainties), one would get a mean for the full sample
of $\mu=2.62\pm0.34$ (shown as a grey band in
Figure~\ref{fig:lensingtest}).  This is separated from the observed SN
magnification by $\delta\mu/\mu=30\%$, which is a 1.7$\sigma$
difference.

The models shown in Figure~\ref{fig:lensingtest} are separated along
the $y$ direction into two broad classes, with the
six \change{so-called} {\it parametrized} models on top and the four
{\it free-form} models on the bottom.\footnote{\change{Although this
nomenclature is becoming standard in the literature, it is somewhat
misleading, as the pixels or grid cells in free-form models are
effectively parameters as well. Perhaps ``simply-parameterized'' would
be more accurate, though we adopt the more common usage here.}}
Broadly speaking, the parametric models use parameterized density
distributions to describe the arrangement of mass within the cluster,
typically associating massive dark matter halos with the positions of
bright cluster member galaxies. Therefore, parametric models rely (to
varying degrees) on the assumption that the observed light from
cluster galaxies is a good tracer of the cluster's dark matter.
Free-form models divide the cluster into a grid, generally using an
adaptive mesh to get better sampling in denser regions. Each grid cell
is assigned a mass or a potential, and then the grid spacing and the
mass values are iteratively refined to match the observed lensing
constraints.

@@

\change{
The traditional color corrections as formalized in SN light curve
fitters are designed to account for a dust component that lies in the
rest frame of the SN.  The inferred luminosity of a SN can also be
affected by the presence of foreground dust with a different redshift
and possibly a different reddening law \citep{Menard:2010b}.  However,
the magnitude of such a bias is insufficient to account for the
observed discrepancy, \citet{Menard:2010a} estimate the opacity of the
universe as $\langle A_{V}\rangle\sim0.03$ mag up to $z=0.5$.  While
this can have a measurable impact on precise cosmological constraints,
it is far less than the 0.285 mag difference between the observed
magnification of \tomas\ and the mean of the model predictions.  
}

@@

\change{
In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
the blue end of the normal range of Type Ia SN colors.  With the SALT2
fitter we measured a color parameter $c=-0.115\pm0.025$, and with
MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
as we are fitting to photometry that covers a rest-frame wavelength
range from $\sim3500-7000$\AA and extends to $\sim$30 days past
maximum brightness.

\textcolor{red}{TODO : discuss 2006bt-like colors}
}

>>>>

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
SN has a projected separation from the cluster core of
$\sim$40\arcsec, closer to the critical lensing line than any previous
cluster-lensed \SNIa.  As such, it provides the first opportunity to
confront gravitational lens models of galaxy clusters with the direct
measurement of an absolute magnification at the edge of the
strong-lensing region.  We derive a tightly constrained measure of the
peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
similar redshift, implying a lensing magnification
of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
measurement of the magnification against predicted magnifications
from \change{14 lens models,} representing a broad range of
methodologies and incorporating a variety of strong- and weak-lensing
constraints.  The models are collectively fairly accurate. \change{
Half of the models deliver median magnifications that are consistent
with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
However, the models are systematically biased to higher values: none
of the tested models predict a magnification equal to or lower than
the observed $\mu$, and some models are more than $5\sigma$ above the
measured magnification.  We evaluate possible causes for this bias,
and find that intercomparison of the lens models rules out several
simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
single cluster could provide a robust evaluation of systematic biases
in lens models.  Until such a sample exists, it is advisable
to \change{increase the estimated uncertainty of predicted
magnifications to match the dispersion observed across multiple lens
models.}
\end{abstract}

@@

\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Li:2012,Quimby:2014}.}

@@

\change{
One of the key values in observing standard candles behind
gravitational lenses is that {\it all} lensing reconstructions suffer
from the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
degeneracy arises because one can introduce into a lens model an
unassociated sheet of mass in front of or behind the lens, without
disturbing the primary observable quantities.  For example, take a
lens model with a given surface mass density $\kappa$, and then
transform the surface mass density to
$\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
$\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$ models will
produce exactly the same values for all positional and shear
constraints from strong and weak lensing.  This is the simplest case
illustrating a positional constraint degeneracy, but there are more
complex versions \citep{Schneider:2014}.  Such mass sheet
degeneracies do not extend to the {\it absolute} magnification of a
background source's flux and size.  Therefore, an absolute measurement
of magnification from a standard candle or a standard ruler
\citep{Sonnenfeld:2011}  can break this fundamental degeneracy
\citep{Holz:2001}.
}

@@

Another nearby bright galaxy to the East of the SN has a spectroscopic
redshift of $z=1.742$.  This redshift was determined from a spectrum
taken with the G141 grism of the HST WFC3-IR camera, collected as part
of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
and \ref{sec:PhotometricClassification}, the SN data are inconsistent
with that redshift, meaning that this nearby galaxy is a background
object and therefore has no impact on the SN magnification.}

@@

\change{
The total uncertainty in the distance modulus is  
}

\begin{equation} \label{eqn:sigmatot}
 \sigma_{\rm tot} = \sqrt{ \sigma_{\rm stat}^2 + \sigma_{int}^2}.
\end{equation}

\change{
\noindent
The $\sigma_{\rm stat}$ term is the statistical uncertainty, which
encapsulates uncertainties from the data and the model, and
$\sigma_{\rm int}$ accounts for the remaining {\it unmodeled} scatter.
This latter term is derived by finding the amount of additional
distance modulus scatter that needs to be added to a Type Ia SN
population to get $\chi^2$ per degree of freedom equal to 1 for a
fiducial cosmological model fit to the SN Ia Hubble diagram (distance
modulus vs redshift).  Thus, $\sigma_{\rm int}$ is designed to
account for any unknown sources of scatter in the Type Ia SN
population, including unidentified errors in the data analysis as well
as the natural scatter in intrinsic Type Ia SN luminosities.  The value of 
$\sigma_{\rm int}$ may be expected to vary as a function of
redshift and also from survey to survey.  
}

\change{
Recent work has highlighted the inadequacy of this simplistic approach
for handling intrinsic scatter in the Type Ia SN
population \citep{Marriner:2011,Kessler:2013,Mosher:2014,Scolnic:2014a,Betoule:2014},
but a full consideration of those alternative approaches is beyond the
scope of this work.  We adopt the simple approach of using a single
empirically defined value for $\sigma_{\rm int}$, reflecting
principally an intrinsic scatter in Type Ia SN intrinsic luminosity
that is fixed across time and phase.  Measurements of $\sigma_{\rm
int}$ range from 0.08 mag \citep{Jha:2007,Conley:2011} to 0.15
mag \citep{Kessler:2009b,Suzuki:2012}.  We adopt a value of
$\sigma_{\rm int}=0.08$ mag, as derived by \citet{Jha:2007}
and \citet{Conley:2011}.  Although this is on the low end of the range
reported in the literature, this value is the most appropriate to
apply to our analysis for two reasons.  First and foremost, for the
SALT2 fitter we are using light curve fit parameters
($\alpha$,$\beta$) with associated uncertainties that have been
derived from the joint analysis of \citet{Conley:2011}
and \citet{Sullivan:2011}. Similarly, the implementation of MLCS2k2
that we have used is based on the uncertainty model derived from model
training in \citet{Jha:2007}.  Inflating $\sigma_{int}$ beyond 0.08
mag would therefore be equivalent to driving the reduced $\chi^2$ of
the Type Ia SN Hubble diagram to $<1$.  Second, the value of 0.08 mag
determined in \citet{Conley:2011} is specific to the HST SN sample,
from \citet{Riess:2007} and \citet{Suzuki:2011}, which is the SN
subset that is most similar to \tomas\ in terms of redshift and data
analysis.  Larger values for $\sigma_{\rm int}$ are typically
associated with SN samples at significantly lower redshifts that have
less homogeneous data collection and analysis. }

\change{
Final values for the SN distance modulus are shown in
Table~\ref{tab:MeasuredMagnification}, adopting the spectroscopic
redshift ($z=1.31$).  In addition to modifying the distance modulus
uncertainty for SN \tomas, we also add $\sigma_{\rm int}=0.08$ mag in
quadrature to the uncertainty for every SN in the control sample. Note
however that the uncertainty on the control sample value at $z=1.31$
is only 0.05 mag, smaller than the intrinsic dispersion because it
reflects only our measurement error on the mean distance modulus of
the population.  The distance moduli derived from the SALT2 and
MLCS2k2 light curve fitters are fully consistent within the
uncertainties.  }

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models. Solid vertical lines show the constraints from SN \tomas\
derived in Section~\ref{sec:Magnification} using the SALT2 (red) and
MLCS2k2 (blue) fitters, with shaded regions marking the total
uncertainty for each. Markers with horizontal error bars show the
median magnification and 68\%\ confidence region from each of the 14
lensing models.  Circles indicate models that use only strong-lensing
constraints, while diamonds denote those that also incorporate
weak-lensing measurements.  Models shown with open markers were
constructed using only data available before the start of the Frontier
Fields observations.  Filled markers indicate models that use
additional input constraints, including new multiply imaged systems
and redshifts.  The seven models shown in black at the top are from
the ``parametric'' family, and the four in green at the bottom are
``free-form.''  The dashed grey line marks the unweighted mean of all
model magnifications.
\label{fig:lensingtest} }
\end{center}
\end{figure}

Table~\ref{tab:PredictedMagnifications} lists the \change{14} models, giving
for each one the predicted magnification and uncertainty for a source
at $z=1.31\pm0.01$ and at the position of \tomas.  These models
represent a broad sampling of the techniques and assumptions that can
be applied to the modeling of mass distributions in galaxy clusters. A
rigorous comparison of these disparate lens modeling techniques is
beyond the scope of this work. Table~\ref{tab:PredictedMagnifications}
includes a brief description of each model, but for a complete
discussion of the methodology the reader is referred to the listed
references.

In Figure~\ref{fig:lensingtest} the model predictions are plotted
alongside the observed magnification of SN \tomas, derived in
Section~\ref{sec:Magnification}.  This comparison shows that these 11
models are largely consistent with each other. Naively treating each
model as an independent prediction for the magnification (and ignoring
their quoted uncertainties), one would get a mean for the full sample
of $\mu=2.51\pm0.34$ (shown as a grey dashed line in
Figure~\ref{fig:lensingtest}).  This is separated from the observed SN
magnification by $\delta\mu/\mu=30\%$, which is a 1.7$\sigma$
difference.

The models shown in Figure~\ref{fig:lensingtest} are separated along
the $y$ direction into two broad classes, with the
six \change{so-called} {\it parametric}\footnote{\change{Although this
nomenclature is becoming standard in the literature, it is somewhat
misleading, as the pixels or grid cells in free-form models are
effectively parameters as well. Perhaps ``simply-parameterized'' would
be more accurate, though we adopt the more common usage here.}}
models on top and the four {\it free-form} models on the bottom.
Broadly speaking, the parametric models use parameterized density
distributions to describe the arrangement of mass within the cluster,
typically associating massive dark matter halos with the positions of
bright cluster member galaxies. Therefore, parametric models rely (to
varying degrees) on the assumption that the observed light from
cluster galaxies is a good tracer of the cluster's dark matter.
Free-form models divide the cluster into a grid, generally using a
\change{multi-scale grid} to get better sampling in denser regions. Each grid cell
is assigned a mass or a potential, and then the mass values are
iteratively refined to match the observed lensing
constraints. \change{In some cases an adaptive grid is used so
that the grid spacing itself can also be modified as the model is
iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.}

@@

\change{
The traditional color corrections as formalized in SN light curve
fitters are designed to account for a dust component that lies in the
rest frame of the SN.  The inferred luminosity of a SN can also be
affected by the presence of foreground dust with a different redshift
and possibly a different reddening law \citep{Menard:2010b}.  However,
the magnitude of such a bias is insufficient to account for the
observed discrepancy, \citet{Menard:2010a} estimate the opacity of the
universe as $\langle A_{V}\rangle\sim0.03$ mag up to $z=0.5$.  While
this can have a measurable impact on precise cosmological constraints,
it is far less than the 0.25 mag difference between the observed
magnification of \tomas\ and the mean of the model predictions.  
}

@@

\change{
In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
the blue end of the normal range of Type Ia SN colors.  With the SALT2
fitter we measured a color parameter $c=-0.115\pm0.025$, and with
MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
as we are fitting to photometry that covers a rest-frame wavelength
range from $\sim3500-7000$\AA and extends to $\sim$30 days past
maximum brightness.  
}

\textcolor{red}{TODO : discuss 2006bt-like colors}
